### 2018-03-29 Datelife_paper1.Rmd
added word

---
output: pdf_document
fontsize: 12pts
textalign: left  # this does not work...
geometry: margin = 1in
bibliography: library.bib
csl: systematic-biology.csl
link-citations: yes
# indent: true # this works
# header-includes:
#    - \setlength\parindent{24pt}  # this works too, but I'mg onna indent manually with 4 spaces
# nope, 4 spaces indents are not recognized, they do something else
linestretch: 2
header-includes:
    - \usepackage[left]{lineno}
    - \linenumbers
---

>>>>

---
bibliography: library.bib
csl: systematic-biology.csl
fontsize: 12pts
geometry: margin = 1in
header-includes:
- \usepackage[left]{lineno}
- \linenumbers
linestretch: 2
link-citations: yes
output:
  word_document: default
  pdf_document: default
textalign: left
---
